---
title: "Refine the Plays"
author: "Amit Kapoor"
date: "6 July 2015"
output: html_document
---

Let's clean the data frame to get the song, artist and url information from the database

```{r}
library(stringr)
library(lubridate)
library(dplyr)

df <- read.csv("data/tweetsdb-2015-07-06-21-40-02.csv",header = TRUE)
str(df)

# Make tweet text as character and fix created time format
df$text <- as.character(df$text)
df$created <- ymd_hms(df$created)
str(df)

# Remove #beats1 from all the text
df$text.tidier <- str_replace_all(df$text, "#beats1", "")

# Extract the url and remove from the list
df$url.raw <- str_extract(df$text.tidier, "https://t.co/[\\w]+")
df$text.tidier <- str_replace_all(df$text.tidier, 
                                  "https://t.co/[\\w]+", "")

# Lets get the song and artist name
# http://stackoverflow.com/questions/24496378/r-using-str-split-and-unlist-to-create-two-columns
# df$song <- str_split(df$text.tidier, "-", n = 2)

df$song <- sapply(strsplit(as.character(df$text.tidier), "-"), "[", 1)
df$artist <- sapply(strsplit(as.character(df$text.tidier), "-"), "[", 2)

# Remove whitespace and format from song and artist name
df$song <- str_to_title(str_trim(df$song))
df$artist <- str_to_title(str_trim(df$artist))

# Create clean song-artist combo with lower case
df$song.artist <- paste0(df$song, " - ", df$artist)

```

There is one more clean up we need to do. The urls are missing for some of the songs observations and avaiable in some other ones. We need to find those missing urls and populate them (where available).

```{r}
# Fill the missing url 
# First create a lookup table where the urls are available
# Note: One potential issue is  that t.co link can shorten the same link in # to two different short links. Need to keep only one.
df.match <- df %>%
            select(song.artist, url.raw) %>%
            filter(!is.na(url.raw)) %>%
            distinct(song.artist)

# Ensure there is only one of them
df.match.count <- df.match %>% 
                  group_by(song.artist) %>%
                  tally(sort = TRUE)

names(df.match)[2] <- "url"

# Join the data frame with left join to get urls
df.full <- left_join(df, df.match, by="song.artist")
```

Lets now save the data into a smaller data frame of what we want - created, song, artist, song.artist and url.

```{r}
# Save a smaller data frame
df.small <- df.full %>%
            select(created, song, artist, song.artist, url)
write.csv(df.small, "data/tweets_processed.csv", row.names = FALSE)

```








